Model-theoretic aspects of relativised cylindric set algebras

### 2020-11-13 problem-9.4/Text.tex
neat embedding stuff (wip)

\begin{enumerate}
\item Suppose $\mathcal{C} \in {\bf RCA}_{\omega}$, whether $\mathcal{C}$ has a complete, $\omega$-dimensional representation?
\item Is the class ${\bf IG}_{\omega}$ (the isomorphism-closure of the $\omega$-dimensional cylindric relativised set algebras in which the unit is closed under substitutions and permutations) a variety, or even
a pseudo-elementary class? Is it closed under ultraproducts?
\end{enumerate}

@@

It is well-known that ${\bf RCA}_{\alpha}$ is a variety, ${\bf RCA}_{\alpha}$ ($\alpha \leq 2$) is finitely axiomatisable and ${\bf RCA}_{\alpha}$ ($2 < \alpha < \omega$) has no finite axiomatisation, see \cite{Henkin1988-HENCAP-4}.

@@

@@

\begin{defin}
  neat embeddable
\end{defin}

>>>>

\begin{enumerate}
\item Suppose $\mathcal{C} \in {\bf RCA}_{\omega}$, whether $\mathcal{C}^{+}$ has a complete, $\omega$-dimensional representation?
\item Is the class ${\bf IG}_{\omega}$ (the isomorphism-closure of the $\omega$-dimensional cylindric relativised set algebras in which the unit is closed under substitutions and permutations) a variety, or even
a pseudo-elementary class? Is it closed under ultraproducts?
\end{enumerate}

@@

It is well known that ${\bf RCA}_{\alpha}$ is a variety, ${\bf RCA}_{\alpha}$ ($\alpha \leq 2$) is finitely axiomatisable and ${\bf RCA}_{\alpha}$ ($2 < \alpha < \omega$) has no finite axiomatisation, see \cite{Henkin1988-HENCAP-4}.

@@

Let us concretise the definition of a canonical extension for $\alpha$-dimensional cylindric algebras:

\begin{defin}
  Let $\mathcal{C} = \langle C, +, -, 0, 1, \{ d_{ij} \}_{i, j < \omega}, \{c_i\}_{i < \omega} \rangle$ be an $\omega$-dimensional cylindric algebra. Let ${\bf Uf}(\mathcal{C})$ be the set of all ultrafilters of $\mathfrak{B}\mathcal{C}$, a Boolean reduct of $\mathcal{C}$.

  Let us define ${\bf C}_{i} : {\bf Uf}(\mathcal{C}) \to {\bf Uf}(\mathcal{C})$ for each $i, j < \omega$ as
  \begin{enumerate}
\item ${\bf C}_{i} \mathcal{X} = \{ \mathcal{F} \in {\bf Uf}(\mathcal{C}) \: | \: \exists \mathcal{F}' \in {\bf Uf}(\mathcal{C}) \: (a \in \mathcal{F} \Rightarrow c_i a \in \mathcal{F}' R)\}$,
\item $D_{ij} = \{ \mathcal{F} \in {\bf Uf}(\mathcal{C}) \: | \: d_{ij} \in \mathcal{F} \}$.
  \end{enumerate}
  The structure $\mathcal{C}^{+} = \langle  {\bf Uf}(\mathcal{C}), \cup, -, \emptyset, C, {\bf C}_{i < \omega}, \{D_{ij}\}_{i, j < \omega} \rangle$ is called the canonical extension of $\mathcal{C}$.
\end{defin}

@@

The following definitions and facts are due to Henkin, Monk, and Tarski \cite{henkin1971cylindric}.

Let $\mathcal{C} = \langle C, +, -, 0, 1, \{d_{ij}\}_{i, j < \beta}, \{ c \}_{c < \beta} \rangle$ be a $\beta$-dimensional cylindic algebra and $\alpha \leq \beta$ an ordinal. The \emph{$\alpha$-th reduct} of $\mathcal{C}$, denoted as $\mathfrak{R}\mathfrak{d}_{\alpha}\mathcal{C}$, is an algebra having the form
\begin{center}
$\mathfrak{R}\mathfrak{d}_{\alpha}\mathcal{C} = \langle C, +, -, 0, 1, \{d_{ij}\}_{i, j < \alpha}, \{ c \}_{c < \alpha} \rangle$
\end{center}

$\mathcal{B}$ is a subreduct of $\mathcal{C}$, denoted as $\mathcal{B} \subseteq^{r} \mathcal{C}$, if $\mathcal{B} \subseteq \mathfrak{R}\mathfrak{d}_{\gamma}\mathcal{C}$ for some $\gamma \leq \beta$.

\begin{defin}
  Let $\mathcal{C}$ be a $\beta$-dimensional cylindic algebra and $\alpha$ an ordinal such that $\alpha \leq \beta$.
  The neat $\alpha$-reduct of $\mathcal{C}$, denoted as $\mathfrak{N}\mathfrak{r}_\alpha \mathcal{C}$,
  is the subalgbera $\mathcal{A}$ of $\mathfrak{R}\mathfrak{d}_{\alpha}\mathcal{C}$ with $\mathcal{A} = \operatorname{Cl}_{\kappa}$ where $\alpha + \kappa = \beta$.

  Let $\mathbb{K}$ be a class of $\beta$-dimensional cylindic algebras, then we put
  \begin{center}
    ${\bf Nr}_{\alpha}\mathbb{K} = \{ \mathfrak{N}\mathfrak{r}_\alpha \mathcal{C} \: | \: \mathcal{C} \in \mathbb{K} \}$
  \end{center}

  An algebra $\mathcal{B}$ is a neat subreduct of $\mathcal{C}$, or $\mathcal{B}$ is neatly embeddable to $\mathcal{C}$ if there exists an ordinal $\gamma \leq \alpha$ such that
  $\mathcal{C} \subseteq \mathfrak{R}\mathfrak{d}_{\gamma}\mathcal{B}$.
\end{defin}
